Comparison with Christensen paper

### 2018-12-26 paper-comparison/compare-christensen.Rmd
Updating with code to run the changepoint-LDA combinations
I'm saving the changepoint models to my computer, because if I put them in the repo it breaks git on my computer. I'm thinking of putting the .Rds files in Dropbox or some other workaround for large files.

### LDATS LDA with LDATS changepoint
```{r, include = F}
# remove paper LDA (for memory)
rm(ldamodel)
```

@@

save(paper_ldats, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda.Rds')

>>>>

### run LDATS LDA with LDATS changepoint
```{r, include = F}
# remove paper LDA (for memory)
rm(ldamodel)
```

@@

save(paper_ldats, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda.Rds') 
```

### run LDATS LDA with paper changepoint

```{r ldats paper, eval = F}
source('christensen-ecology-files/changepointmodel.r')
# set up parameters for model
year_continuous = 1970 + as.integer(julian(ch_dates)) / 365.25
x = data.frame(
  year_continuous = year_continuous,
  sin_year = sin(year_continuous * 2 * pi),
  cos_year = cos(year_continuous * 2 * pi)
)

# run models with 1, 2, 3, 4, 5 changepoints
cp_results_rodent = changepoint_model(ldats_lda_selected[[1]], x, 1, weights = rep(1,length(year_continuous)))

save(cp_results_rodent, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda1.Rds')
rm(cp_results_rodent)

cp_results_rodent2 = changepoint_model(ldats_lda_selected[[1]], x, 2, weights = rep(1,length(year_continuous)))

save(cp_results_rodent2, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda2.Rds')
rm(cp_results_rodent2)

cp_results_rodent3 = changepoint_model(ldats_lda_selected[[1]], x, 3, weights = rep(1,length(year_continuous)))
save(cp_results_rodent3, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda3.Rds')
rm(cp_results_rodent3)

cp_results_rodent4 = changepoint_model(ldats_lda_selected[[1]], x, 4, weights = rep(1,length(year_continuous)))
save(cp_results_rodent4, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda4.Rds')
rm(cp_results_rodent4)

cp_results_rodent5 = changepoint_model(ldats_lda_selected[[1]], x, 5, weights = rep(1,length(year_continuous)))
save(cp_results_rodent5, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda5.Rds')
rm(cp_results_rodent5)

cp_results_rodent6 = changepoint_model(ldats_lda_selected[[1]], x, 6, weights = rep(1,length(year_continuous)))
save(cp_results_rodent6, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda6.Rds')
rm(cp_results_rodent6)

rm(ldats_lda_selected)
```

### run paper LDA with paper changepoint
```{r paper paper, eval = F}
source('christensen-ecology-files/changepointmodel.r')
# set up parameters for model
year_continuous = 1970 + as.integer(julian(ch_dates)) / 365.25
x = data.frame(
year_continuous = year_continuous,
sin_year = sin(year_continuous * 2 * pi),
cos_year = cos(year_continuous * 2 * pi)
)
# run models with 1, 2, 3, 4, 5 changepoints
cp_results_rodent = changepoint_model(ldamodel, x, 1, weights = rep(1,length(year_continuous)))
save(cp_results_rodent, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda1.Rds')
rm(cp_results_rodent)

cp_results_rodent2 = changepoint_model(ldamodel, x, 2, weights = rep(1,length(year_continuous)))
save(cp_results_rodent2, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda2.Rds')
rm(cp_results_rodent2)

cp_results_rodent3 = changepoint_model(ldamodel, x, 3, weights = rep(1,length(year_continuous)))
save(cp_results_rodent3, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda3.Rds')
rm(cp_results_rodent3)

cp_results_rodent4 = changepoint_model(ldamodel, x, 4, weights = rep(1,length(year_continuous)))
save(cp_results_rodent4, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda4.Rds')
rm(cp_results_rodent4)

cp_results_rodent5 = changepoint_model(ldamodel, x, 5, weights = rep(1,length(year_continuous)))
save(cp_results_rodent5, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda5.Rds')
rm(cp_results_rodent5)

cp_results_rodent6 = changepoint_model(ldamodel, x, 6, weights = rep(1,length(year_continuous)))
save(cp_results_rodent6, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda6.Rds')
rm(cp_results_rodent6)
```

### run paper LDA with LDATS changepoint
```{r paper ldats, eval = F}
# Run changepoint

paper_ldats <- LDATS::TS_on_LDA(LDA_models = ldamodel,
                                document_covariate_table = rodents[[2]],
                                formulas =c(~ sin_year + cos_year),
                                nchangepoints = c(2, 3, 4, 5, 6),
                                weights = NULL)

save(paper_ldats, file = 'model-stash/paper_ldats.Rds')

paper_ldats_selected <- LDATS::select_TS(TS_models = paper_ldats)

save(paper_ldats_selected, file = '/Users/renatadiaz/Documents/model-stash/paper_ldats_selected.Rds')
